The Diminishing Returns of Music in the Digital Era

### 2024-04-18 paper/paper.qmd
adding .gitignore and other small edits

bayesian_model <- brm(value_actual ~ format, data = music_data, 
                      family = gaussian(), 
                      prior = c(set_prior("normal(0, 10)", class = "b"),
                                set_prior("cauchy(0, 2)", class = "sigma")),
                      chains = 4, iter = 2000, warmup = 500, 
                      control = list(adapt_delta = 0.95),
                      refresh = 0)
```

>>>>

bayesian_model <- brm(value_actual ~ format, data = music_data, 
                      family = gaussian(), 
                      prior = c(set_prior("normal(0, 10)", class = "b"),
                                set_prior("cauchy(0, 2)", class = "sigma")),
                      chains = 4, iter = 2000, warmup = 500, 
                      control = list(adapt_delta = 0.95),
                      refresh = 0)
saveRDS(bayesian_model, file = "first_model.rds")
```
